Simulations log

### 2020-05-14 results/README.Rmd
update simulations

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and `.json` statistics files produced by the two jupyter notebooks above. The plots are used in the manuscript, the data are further processed by this readme into tables before they are manuscript-ready.
- `README.Rmd` containing R-code to transform the `.json` files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as `.RDS` files.

@@

@@

# ATD needs to be adjusted for 1 prior inclusion and 1 prior exclusion! 
# compute adjusted ATD to make it equal to the area above the curve
datastats <- readRDS("datastats.RDS") %>%
  select(Dataset, candidates_test, incl_test) %>%
  # account for 1 prior exclusion and 1 prior inclusion
  mutate(n_1 = incl_test, n_excl = candidates_test-n_1, n_1_noprior = incl_test-1, candidates_noprior = candidates_test -1) %>%
  mutate(ratio = (n_1_noprior/n_1)/(candidates_noprior/candidates_test))

>>>>

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the `.h5` simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and `.json` statistics files produced by the two jupyter notebooks above. The plots are used in the manuscript, the data are further processed by this readme into tables before they are manuscript-ready.
- `README.Rmd` containing R-code to transform the `.json` files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as `.RDS` files.  
- the `datastats.RDS` is used in the analyses to compute adjusted ATD values (see code below)

@@

# Reproduce data extraction
To reproduce the results, follow the steps below. If you do not want to download the raw simulation output, start at step 3:

1. Run all code in the `extract_plots.ipynb` notebook to create all plots. This requires having the raw simulation data, to be found on the OSF (https://osf.io/7mr2g/ and https://osf.io/ag2xp/). Note that you will need to adjust the paths to where you've stored the simulation output on your local computer. Also, note that creating figures can take quite some time, depending on your computer. Mine took from 30 minutes to 5 hours per figure The final figures can be found in the `one_seed/plots` directory. 
2. Run all code in the `extract_results.ipynb` to extract the metrics WSS, RRF and ATD from the raw simulation data. Note that you will need to adjust the paths to where you've stored the simulation output on your local computer. Also, note that extracting all results will take quite some time, depending on your computer. Mine took 48 hours. The results are stored in the `one_seed/plots` directory. 
3. Follow the preprocessing steps in the `README.Rmd` files to create tables for in the manuscript, stored in the `output` directory.

@@

  return(dat)
}
```

The ATD values need to be adjusted for prior inclusions and exclusions as the computation does not take into account that prior to the active learning cycle, already 1 inclusion and 1 exclusion have been labelled 'for free'. 
```{r}
# ATD needs to be adjusted for 1 prior inclusion and 1 prior exclusion! 
# compute adjusted ATD to make it equal to the area above the curve
datastats <- readRDS("datastats.RDS") %>%
  select(Dataset, candidates_test, incl_test) %>%
  # account for 1 prior exclusion and 1 prior inclusion
  mutate(n_1 = incl_test, n_excl = candidates_test-n_1, n_1_noprior = incl_test-1, candidates_noprior = candidates_test -1) %>%
  mutate(ratio = (n_1_noprior/n_1)/(candidates_noprior/candidates_test))

### 2020-05-14 simulation_study/README.Rmd
update simulations

```{r, include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
#source("R/00_condition_grid.R")
```

# Models 
We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
```{r, eval = TRUE}
conditiongrid <- readRDS("R/00_conditiongrid.RDS")
conditiongrid <- conditiongrid[c(1:4,7:9),]
conditiongrid %>%
  mutate(Model = c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )) %>%
  mutate(Abbreviation = condition) %>%
  select(Model, Abbreviation) %>%
  kable(format = "markdown")
```
The first letter denotes the classification strategy, NB, LR, RF, or SVM. The second letter stands for C of certainty sampling. The third letter denotes the feature extraction strategy, TF-IDF or Doc2vec. The fourth letter stands for D of Dynamic Resampling.

@@

And then, within the newly created directory, the following:
```{bash, eval = FALSE}
# install visualization package 
pip install . 
```

>>>>

```{r, include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
#source("R/00_condition_grid.R")
```
# Content 
This repository contains:

- `hpoptimization` documentation on how hyperparameters were optimized plus the resulting parameters.
- `simulation` documentation on how the models were simulated on the systematic review datasets. 
- `R` containing R-scripts called upon in the current readme, to structure the whole simulation process.

To reproduce the research, first follow the steps in `hpoptimization`, then those in `simulation`. If you wish to skip the hyperparameter optimization step, this is possible since the results of the hyperparameter optimization are available in this repository.

# Models 
We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
```{r, eval = TRUE, echo = FALSE}
conditiongrid <- readRDS("R/00_conditiongrid.RDS")
conditiongrid <- conditiongrid[c(1:4,7:9),]
conditiongrid %>%
  mutate(Model = c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )) %>%
  mutate(Abbreviation = condition) %>%
  select(Model, Abbreviation) %>%
  kable(format = "markdown")
```
The first letter denotes the classification strategy, NB, LR, RF, or SVM. The second letter stands for C of certainty sampling. The third letter denotes the feature extraction strategy, TF-IDF or Doc2vec. The fourth letter stands for D of Dynamic Resampling.

@@

And then, within the newly created directory, the following:
```{bash, eval = FALSE}
pip install . 
```

### 2020-05-14 simulation_study/simulation/README.Rmd
update simulations

---
title: "Simulations log"
output: github_document
---

This directory contains all scripts used to simulate systematic reviews. 
Note that the files resulting from this simulation are enormous (over 500GB in total), therefore they cannot be stored on GitHub. Instead, those files are published on the Open Science Framework, divided over 2 ..

- `scripts` -  contains all scripts run on the Cartesius supercomputer. The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
- `config` - contains the hyperparameters for every model-dataset combination. These files are called upon in the simulation command.

If you want to run a simulation locally, for example the NB + TF-IDF model on the nudging run the following in your bash terminal:

```{bash, eval = FALSE}

```

The simulation will output one or more `.h5` files (depending on the number of trials you choose). Please refer to the `results` folder in the root directory of this repository for a demonstration of how to analyze the resulting files.

>>>>

---
title: "Simulations"
output: github_document
---

This directory contains all scripts used to simulate systematic reviews:

- `config` - contains the hyperparameters for every model-dataset combination. These files are called upon in the simulation command. They are copies from the config files in the `hpoptimization/config` directory, except that the `n_instances` parameter has been set to 1, so that the model is retrained after labelling one publication instead of 20. 
- `scripts` -  contains all scripts run on the Cartesius supercomputer. The `log.Rmd` file tracks when all these scripts were executed and connects them to a jobID on Cartesius (just for documentation).
- `simoutput` - where the output of the simulation files is stored. As mentioned in the readme in the root directory, the files resulting from this simulation are enormous (over 500GB in total), therefore they cannot be stored on GitHub and the `simoutput` directory remains empty. Instead, the simulation output files are published on the Open Science Framework: https://osf.io/7mr2g/ and https://osf.io/ag2xp/.

## Running a simulation
All simulations were run with seed value `42`. If you want to run a simulation locally, for example the NB + TF-IDF model on the nudging dataset, for 15 trials, run the following in your bash terminal:

```{bash, eval = FALSE}
asreview batch ../../datasets/sim_datasets/nudging.csv --config_file config/one/BCTD/nb_max_double_tfidf-nudging.ini --state_file simoutput/one/BCTD/nudging/results.h5 -r 15 --init_seed 42
```

The simulation will output 15 `.h5` files. Please refer to the `results` folder in the root directory of this repository for a demonstration of how to analyze the resulting files. Code for processing these files can be found in the `results` directory, which also contains already A processed version of the simulation output files is available in the `results` directory.

### 2020-05-14 simulation_study/simulation/log.Rmd
update simulations

# SCTD 
# ace ptsd software
sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
names(sctd) <- c("8025808", "8025809", "8025810")
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
createLines("SCTD", "ptsd", "one") # 8066095
createLines("SCTD", "software", "one")
```

---

>>>>

# SCTD 
# ace ptsd software
sctd <- createLines("SCTD", c("ace", "ptsd", "software"), "one")
names(sctd) <- c("8025808", "8025809", "8025810")
#scp -r gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/simoutput/one/SCTD/ace /Volumes/Gerbrich/asreview/simoutput/one/SCTD
createLines("SCTD", "ptsd", "one") # 8066095
createLines("SCTD", "software", "one")
```
---
